Meta-analysis fear learning

### 2022-03-02 manuscript/manuscript.Rmd
update 2022-03-02 15:25:16

```{r, results="asis"}
print("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.")
```

@@

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  if(nrow(df) == 0) return(NULL)
  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
    v <- df[[n]]
    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
    droplevels(v)
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  # names(refcat) <- c("Variable", "Reference")
  df_mods <- df[mods]
  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
  df_mods <- df_mods[, !constcols, drop = FALSE]
  modmat <- model.matrix(~., df_mods)
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  saveRDS(res, paste0("rma_", p, ".RData"))
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

@@

  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
  saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
  moddatvi <- moddat$vi
  moddat <- moddat[, -which(colnames(moddat) == "vi")]
  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
  list(rma = tabres,
       brma = sumpma,
       mc = resmc)
})
names(modres) <- processes
saveRDS(modres, "modres.RData")
```

>>>>

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.**")
```

@@

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  print(p)
  df <- dat[dat$Process == p, ]
  if(nrow(df) == 0) return(NULL)
  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
    v <- df[[n]]
    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
    droplevels(v)
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  # names(refcat) <- c("Variable", "Reference")
  df_mods <- df[mods]
  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
  df_mods <- df_mods[, !constcols, drop = FALSE]
  modmat <- model.matrix(~., df_mods)
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols, drop = FALSE]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols, drop = FALSE]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  saveRDS(res, paste0("rma_", p, ".RData"))
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

@@

  pma <- try({brma(yi ~., study = "study", data = moddat, standardize = standardize)})
  if(inherits(pma, "try-error")){
    pma <- NULL
    sumpma <- data.frame(NA, NA)
  } else {
    saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
  }

  moddatvi <- moddat$vi
  moddat <- moddat[, -which(colnames(moddat) == "vi")]
  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
  list(rma = tabres,
       brma = sumpma,
       mc = resmc)
})
names(modres) <- processes
saveRDS(modres, "modres.RData")
```

### 2022-03-02 manuscript/sensitivity_Camp20121.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = FALSE
sens_papers <- "{{sens_study}}" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study {{sens_study}} has been removed from the data.**")
```

@@

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  print(p)
  df <- dat[dat$Process == p, ]
  if(nrow(df) == 0) return(NULL)
  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
    v <- df[[n]]
    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
    droplevels(v)
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  # names(refcat) <- c("Variable", "Reference")
  df_mods <- df[mods]
  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
  df_mods <- df_mods[, !constcols, drop = FALSE]
  modmat <- model.matrix(~., df_mods)
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols, drop = FALSE]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols, drop = FALSE]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  saveRDS(res, paste0("rma_", p, ".RData"))
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

@@

  pma <- try({brma(yi ~., study = "study", data = moddat, standardize = standardize)})
  if(inherits(pma, "try-error")){
    pma <- NULL
    sumpma <- data.frame(NA, NA)
  } else {
    saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
  }

  moddatvi <- moddat$vi
  moddat <- moddat[, -which(colnames(moddat) == "vi")]
  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
  list(rma = tabres,
       brma = sumpma,
       mc = resmc)
})
names(modres) <- processes
saveRDS(modres, "modres.RData")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (1)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (1) has been removed from the data.**")
```

@@

```{r, eval = run_everything}
library(metacart)
modres <- lapply(processes, function(p){
  df <- dat[dat$Process == p, ]
  if(nrow(df) == 0) return(NULL)
  df[refcat$Variable] <- lapply(refcat$Variable, function(n){
    v <- df[[n]]
    v <- relevel(v, ref = refcat$Reference[refcat$Variable == n])
    droplevels(v)
  })
  # refcat <- data.frame(do.call(rbind,lapply(names(df[catvars]), function(n){c(n, levels(df[[n]])[1])})))
  # names(refcat) <- c("Variable", "Reference")
  df_mods <- df[mods]
  constcols <- sapply(df_mods, function(i){length(unique(i))}) == 1
  df_mods <- df_mods[, !constcols, drop = FALSE]
  modmat <- model.matrix(~., df_mods)
  constcols <- colSums(modmat) == 0 | colSums(modmat) == nrow(modmat)
  constcolnames <- colnames(modmat)[constcols]
  modmat <- modmat[, !constcols]
  modmatlist <- as.list(data.frame(modmat))
  dupcols <- duplicated(modmatlist)
  modmat <- modmat[, !dupcols]
  these_dups <- modmatlist[dupcols]
  modmatlist <- as.list(data.frame(modmat))
  for(i in 1:length(these_dups)){
    idnum <- which(duplicated(c(modmatlist, these_dups[i]), fromLast = T))
    colnames(modmat)[idnum] <- paste0(colnames(modmat)[idnum], ";", names(these_dups)[i])
  }
  yi_notcentered <- df$yi# - mlm[[p]]$mod$b[1,1]
  res <- rma(yi = yi_notcentered,
             vi = df$vi,
             mods = modmat)
  vifs <- vif(res)
  saveRDS(res, paste0("rma_", p, ".RData"))
  tabres <- data.frame(Parameter = c(rownames(res$b), "Tau2"),
                       cbind(
                         Estimate = c(res$b, res$tau2),
                         se = c(res$se, res$se.tau2),
                         ci.lb = c(res$ci.lb, res$tau2-1.96*res$se.tau2),
                         ci.ub = c(res$ci.ub, res$tau2+1.96*res$se.tau2),
                         p = c(res$pval, res$QEp)))
  tabres$CI <- conf_int(lb = tabres$ci.lb, ub = tabres$ci.ub)
  tabres[c("ci.lb", "ci.ub")] <- NULL
  tabres$VIF <- c(NA, vifs$vif, NA)
  write.csv(tabres, paste0("rma_mods_", p, ".csv"))

@@

  pma <- brma(yi ~., study = "study", data = moddat, standardize = standardize)
  saveRDS(pma, paste0("pma_", p, ".RData"))
  sumpma <- data.frame(summary(pma)$coefficients)
  sumpma <- cbind(rownames(sumpma), sumpma)
  names(sumpma)[1:3] <- c("Parameter", "Estimate", "se")
  sumpma <- sumpma[!sumpma$Parameter == "tau", ]
  rownames(sumpma) <- NULL
  sumpma$CI <- conf_int(lb = sumpma$X2.5., ub = sumpma$X97.5.)
  pstars <- c("*", "")[as.integer(apply(sumpma[, c("X2.5.", 
                                                   "X97.5.")], 1, function(x) {
                                                     sum(sign(x)) == 0
                                                   })) + 1]
  sumpma$p <- pstars
  sumpma[c("sd", grep("^X", names(sumpma), value = T))] <- NULL
  write.csv(sumpma, paste0("brma_mods_", p, ".csv"))
  moddatvi <- moddat$vi
  moddat <- moddat[, -which(colnames(moddat) == "vi")]
  resmc <- suppressWarnings(metacart::FEmrt(reformulate(mods, response = "yi"), data = df, vi = df$vi))
  list(rma = tabres,
       brma = sumpma,
       mc = resmc)
})
names(modres) <- processes
saveRDS(modres, "modres.RData")
```

### 2022-03-02 manuscript/sensitivity_Camp20122.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (1)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (1) has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (2)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (2) has been removed from the data.**")
```

### 2022-03-02 manuscript/sensitivity_Camp20123.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (2)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (2) has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (3)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (3) has been removed from the data.**")
```

### 2022-03-02 manuscript/sensitivity_Camp20124.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (3)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (3) has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (4)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (4) has been removed from the data.**")
```

### 2022-03-02 manuscript/sensitivity_Fitzgerald2015.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Camp 2012 (4)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Camp 2012 (4) has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Fitzgerald 2015" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Fitzgerald 2015 has been removed from the data.**")
```

### 2022-03-02 manuscript/sensitivity_Gottschalk2018.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Fitzgerald 2015" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Fitzgerald 2015 has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Gottschalk 2018" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Gottschalk 2018 has been removed from the data.**")
```

### 2022-03-02 manuscript/sensitivity_Ju2017.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Gottschalk 2018" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Gottschalk 2018 has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Ju 2017" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Ju 2017 has been removed from the data.**")
```

### 2022-03-02 manuscript/sensitivity_Xiong20151.Rmd
update 2022-03-02 15:25:16

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Ju 2017" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Ju 2017 has been removed from the data.**")
```

>>>>

```{r setup, include=FALSE}
run_everything = TRUE
sensitivity = TRUE
sens_papers <- "Xiong 2015 (1)" #c("Camp 2012 (1)", "Camp 2012 (2)", "Camp 2012 (3)", "Camp 2012 (4)", "Fitzgerald 2015", "Gottschalk 2018", "Ju 2017", "Xiong 2015 (1)", "Xiong 2015 (2)")
library("worcs")
library(ggplot2)
library(kableExtra)
library(DT)
library(tidySEM)
library(knitr)
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
```

@@

```{r, results = "asis"}
cat("**This is a sensitivity analysis; the study Xiong 2015 (1) has been removed from the data.**")
```
